Seasonality of submesoscale dynamics in the Kuroshio Extension

### 2016-09-21 writeup/RochatEtal_ResponseToReviewers.tex

        \bdp
          We explicitly state that those are submesoscale IGWs. Using
          our definition of submesoscales, these are IGWs
          with horizontal scales about 10-100 km\footnote{Bill Young suggested the
          term submesoscale IGWs.}; IGWs have periods between the inertial and buoyancy
          periods.  The GM spectrum is inaccurate
          close to the surface (most of our results concern surface currents and SSH,
          and it does not account for tidal and inertial peaks. We believe that the
          new plot of the wavenumber-frequency spectrum of the SSH
          variance (new Figure 4) --- following the reviewer's suggestion ---
          will more clearly convey the idea that there is no horizontal scale
          separation between submesoscale IGWs and submesoscale turbulence.\\

          If the reviewer is using ``balanced'' as a shorthand to ``geostrophically
          and hydrostatically
          balanced'', then the comment about the GM spectrum containing both balanced
          and unbalanced flows is incorrect.  GM used linear theory
          of IGW to synthesize observations, mostly mooring data, in the IGW band
           --- they
          fitted an analytic model to (super-inertial) frequency spectra and
          different vertical modes \citep[see][and references therein]{munk1981}.
          One could argue
          that other flows project onto similar temporal scales, but those motions
          are super-inertial (e.g., stratified turbulence), not (sub-inertial)
          balanced flows.
        \edp

 \item {\it Discretization of the underlying equations of motion. How do you expect the
        combination of vertical and horizontal resolution modifies internal wave properties
        that exist in your model? Might you be attributing characteristics to these waves that
        would be different in the real ocean?}\\

        The model resolves IGWs well, particularly those waves with periods larger
        than 1h considered in this paper --- we are restricted to the output
        frequency. Higher-frequency waves that project onto lateral scales smaller
        than 10 km are potentially inaccurate but strongly damped in our simulations.

@@

      We rewrote that sentence.

\item {\it 24. (Section 3, Paragraph 1) ``These diagnostic highlight the submesoscale structures in
      the flow.'' It might help the authors to motivate their calculations using the following:}\\

      {\it ``Any horizontal velocity field, uh, can be expressed in terms of vorticity, divergence,
      strain rate and mean flow. This can be seen by expressing uh as a Taylor series
      expansion and then decomposing the velocity gradient into symmetric and anti-
      symmetric parts [Landau and Lifshitz, 1987]. Because vortices, vertical motion and
      fronts are ubiquitous at the submesoscale, this is a natural decomposition and
      variances of these quantities are apt descriptors of submesoscale turbulence.''}\\

      \bdp
        We included a brief description/motivation for the use of second-order statistics
        of those quantities. Thanks for pointing this out.
      \edp

### 2016-09-21 writeup/rocha_etal.tex
Minor changes

\section{Bulk statistics of the surface lateral velocity gradient tensor}
To study the seasonality in the surface velocity, we calculate the lateral velocity gradient tensor
\begin{equation}
\left[\begin{matrix} u_x & u_y\\ v_x&v_y \end{matrix}\right]
\end{equation}
using a centered
second-order finite difference scheme. We then diagnose
the vertical vorticity
\begin{equation}
\zeta \equiv v_x - u_y\, ,
\end{equation}
lateral rate of strain
\begin{equation}
  \alpha \equiv [(u_x-v_y)^2 + (u_y + v_x)^2]^{1/2}\,,\\
\end{equation}
and horizontal divergence
\begin{equation}
\delta \equiv u_x + v_y\, .
\end{equation}
These diagnostics highlight the submesoscale structures in the flow
\citep[e.g.,][]{shcherbina_etal2013}.

>>>>

\section{Bulk statistics of the surface lateral velocity gradient tensor}
To study the seasonality in the surface velocity, we calculate the lateral velocity gradient tensor
\begin{equation}
\left[\begin{matrix} u_x & u_y\\ v_x&v_y \end{matrix}\right]
\end{equation}
using a centered
second-order finite difference scheme. We then diagnose
the vertical vorticity
\begin{equation}
\zeta \equiv v_x - u_y\, ,
\end{equation}
lateral rate of strain
\begin{equation}
  \alpha \equiv [(u_x-v_y)^2 + (u_y + v_x)^2]^{1/2}\,,\\
\end{equation}
and horizontal divergence
\begin{equation}
\delta \equiv u_x + v_y\, .
\end{equation}
Because vortices, fronts, and IGWs are ubiquitous at submesoscales, second-order
statistics of vorticity, strain, and divergence are apt descriptors of these
fine lateral scales \citep[e.g.,][]{shcherbina_etal2013}.
